---
title: "Pokemon"
subtitle: "Tidy Tuesday Week 13"
author: "Nicole Bonge"
toc: true
toc-location: right-body
number-sections: true
date-modified: last-modified
date-format:  "MM/DD/YYYY"
format: pdf
  
---
# Motivation

Pokemon is a global icon. It is a TV series that expanded into video games, Pokemon cards/collectibles, and merchandise that made it into a multimillion dollar franchise. Growing up, Pokemon was one of my favorite shows and to this day, it remains one of the fondest memories from my childhood.

# Research Question

Before I begin my project, I should know what I am doing and how to do it. This quarter, I am in my first *Introduction to R* course so my project directly applies the course material. I utilized my lecture notes to learn the technicalities of coding it and the mathematics behind each line I wrote.

After doing my research, I took this approach to solve my own problem: **Could I predict battle outcomes?**

My report is organized into the following section:

1. Loading the Data Set

2. Data Visualization

3. Linear Regression.

## Data Visualization

Data visualization is a powerful tool. @fig-boxplot shows the characteristics by their Types.


```{r}
#| message: false
#| echo: false
#| fig-cap: "Boxplot of denfense and attack by their types"
#| label: fig-boxplot
source("ttw13-pokemon.R")
fig1
```


Second, I check out the relationships among six dimensions of information of Pokemon using pairwise scatterplot. As shown in @fig-scatter, I did not see clear relationships.
```{r}
#| message: false
#| echo: false
#| fig-cap: "Pairwise scatterplot"
#| label: fig-scatter
fig2
```
## Linear Regression Results
```{r}
#| echo: false
#| label: tbl-regression
#| tbl-cap: "Linear regression of six indices on HP"
kableExtra::kable(tbl1)
```
As @tbl-regression shows, *Speed* and *Defense* have negative effects on *HP*, while *Attack* has positive effect on Pokemon's HP. *Defense* has no significant relationship with *HP*.

## Conclusion

With this project, I achieved a lot of firsts. It was the first time that I worked with such a large dataset. Not only were there 800 observations, but there were also 12 different variables. This meant I had a lot to play around with and explore, but also there was room for a lot of error.

It was also the first time I have worked with multiple linear regression. I am accustomed to performing linear regression analysis on the relationship between two variables, so working with eight was a new challenge.
